Testing atlantisom: generate census length comps

### 2019-05-09 TrueLengthCompTest.Rmd
more refinements

So, test 1 is running `calc_age2length` with the full true dataset. This should work because there will be no aggregation of the output (no, don't do this with the full dataset! example with one species instead):

@@

atf_length_census <- calc_age2length(structn = atf_truestructn,
                                 resn = atf_trueresn,
                                 nums = atf_truenums,
                                 biolprm = truth$biolprm, fgs = truth$fgs,
                                 CVlenage = 0.1, remove.zeroes=TRUE)

@@

This produced output for a single species by mistake. It ran for hours on the full truth dataset and did not complete (I stopped it). Its doing it for all species, which is a problem. Rewrote for just one species to see full length comp by area and depth layer.

@@

@@

Try again with survey sampling for nums, structn and resn, which limits the species list to fish and sharks, and also aggregates over layer and polygon. Test this:

@@

>>>>

So, test 1 is running `calc_age2length` with the full true dataset. This should work because there will be no aggregation of the output (no, don't do this with the full dataset! example with one species instead. actually, don't even try this):

@@

#atf_length_census <- calc_age2length(structn = atf_truestructn,
#                                 resn = atf_trueresn,
#                                 nums = atf_truenums,
#                                 biolprm = truth$biolprm, fgs = truth$fgs,
#                                 CVlenage = 0.1, remove.zeroes=TRUE)
atf_length_census <- lenout

@@

This produced output for a single species by mistake. It ran for hours on the full truth dataset, and on the just arrowtooth full truth dataset and did not complete (I stopped it). Testing for just one species and 500 index steps (of 103690) to see full length comp by area and depth layer.

@@

lfplot <- ggplot(atf_length_census$natlength, aes(upper.bins)) +
  geom_bar(aes(weight = atoutput)) +
  theme_tufte()

lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 1)
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 2)
lfplot + facet_wrap_paginate(~time, ncol=4, nrow = 4, page = 3)

lfplot + facet_wrap_paginate(~polygon, ncol=4, nrow = 4, page = 1)
lfplot + facet_wrap_paginate(~polygon, ncol=4, nrow = 4, page = 2)
lfplot + facet_wrap_paginate(~polygon, ncol=4, nrow = 4, page = 3)

@@

Try again with survey sampling for nums, structn and resn, which limits the species list to fish and sharks, and also aggregates over layer and polygon. This will still take too long. Can we run with the sample_fish in nums? Test this:

@@

#cut down to single species
atf_survey_teststructnall <- survey_teststructnall[survey_teststructnall$species == "Arrowtooth_flounder",]
atf_survey_testresnall <- survey_testresnall[survey_testresnall$species == "Arrowtooth_flounder",]
atf_survey_testNall <- survey_testNall[survey_testNall$species == "Arrowtooth_flounder",]
